Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-03-17 xrb3/paper.tex
Add me as co-author
add helmeos to softwar

@@

\begin{acknowledgements}
\castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setup used
here is available in the git repo as {\tt flame\_wave}. The metadata
describing the build environment and the global diagnostic output
files are available on Zenodo at \citet{xrb_data}.  We thank Alice
Harpole and Max Katz for their contributions to the AMReX Astrophysics
suite.

@@

\software{\amrex~\citep{amrex_joss},
          \castro~\citep{castro,castro_joss},
          GCC (\url{https://gcc.gnu.org/}),
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}

>>>>

\author[0000-0003-0439-4556]{Max Katz}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
             Stony Brook, NY 11794-3800}

@@

\begin{acknowledgements}
\castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setup used
here is available in the git repo as {\tt flame\_wave}. The metadata
describing the build environment and the global diagnostic output
files are available on Zenodo at \citet{xrb_data}.  We thank Alice
Harpole for contributions to the AMReX Astrophysics suite.

@@

\software{\amrex~\citep{amrex_joss},
          \castro~\citep{castro,castro_joss},
          GCC (\url{https://gcc.gnu.org/}),
          helmeos \citep{timmes_swesty:2000},
          linux (\url{https://www.kernel.org/}),
          matplotlib (\citealt{Hunter:2007}, \url{http://matplotlib.org/}),
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          valgrind \citep{valgrind},
          VODE \citep{vode},
          yt \citep{yt}}
